---
title: "fidelity"
author: "Jingning Yang"
date: "11/8/2019"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Import dataset(selected fund the indices data from )

```{r cars}
library(tidyverse)
library(dplyr)
library(tidyr)
library(magrittr)
library(ggplot2)

data <-read.csv("FIVFX-4.csv",header = TRUE, sep = ",")
EEM <- read.csv("EEM.csv",header = TRUE, sep = ",")
JFAMX <- read.csv("JFAMX.csv",header = TRUE, sep = ",")
MOAT <- read.csv("MOAT.csv",header = TRUE, sep = ",")
GSPC <- read.csv("^GSPC-2.csv",header = TRUE, sep = ",")
```
# Format date 
```{r}
data$Date<- as.Date(data$Date, "%Y-%m-%d")
EEM$Date<- as.Date(EEM$Date, "%Y-%m-%d")
JFAMX$Date<- as.Date(JFAMX$Date, "%Y-%m-%d")
MOAT$Date<- as.Date(MOAT$Date, "%Y-%m-%d")
GSPC$Date<- as.Date(GSPC$Date, "%Y-%m-%d")
```

# Choose variables we need(Date and Close price daily)

```{r pressure, echo=FALSE}

data %<>% select(Date, Close) %>% rename(FIVFX=Close) 
EEM %<>% select(Date, Close) %>% rename(EEM=Close)
JFAMX %<>% select(Date, Close) %>% rename(JFAMX=Close) 
MOAT %<>% select(Date, Close) %>% rename(MOAT=Close) 
GSPC %<>% select(Date, Close) %>% rename(GSPC=Close) 

```

# Merge indices and fund data into one table with same time line
```{r}
com <- merge(data, JFAMX, by="Date")
com <- merge(com, EEM, by= "Date")
com <- merge(com, MOAT, by="Date")
com <- merge(com, GSPC, by="Date")
com$Date <- as.Date(com$Date, format='%Y-%m-%d')
```

# Visualize indices and fund data's close price in the same time line
```{r}
ggplot(com) + 
  geom_line(aes(x=Date, y=(com$EEM)), color = "brown") +
  geom_line(aes(x=Date, y=(com$FIVFX)), color = "red") +
  geom_line(aes(x=Date, y=(com$JFAMX)), color = "purple") +
  geom_line(aes(x=Date, y=(com$MOAT)), color = "black") 
```



# Form a table contains the log return of indices and fund close price 
```{r}
EEM_r <- diff(log(com$EEM), differences = 1)
FIVFX_r <- diff(log(com$FIVFX), differences = 1)
JFAMX_r <- diff(log(com$JFAMX), differences = 1)
MOAT_r <- diff(log(com$MOAT), differences = 1)
GSPC_r <- diff(log(com$GSPC), differences = 1)
log <- data.frame(cbind(FIVFX_r, EEM_r, MOAT_r, JFAMX_r, GSPC_r))
log <- cbind(com$Date[2:length(com$Date)], log)
names(log)[1] <- "Date"
```

# Visulize Daily log retrun of funds and indices in same time line
```{r}
ggplot(com)+
  geom_line(aes(x=Date, y=1000*(FIVFX/com$FIVFX[1]))) +
  geom_line(aes(x=Date, y=1000*(EEM/com$EEM[1]), color="brown"))+
  geom_line(aes(x=Date, y=1000*(JFAMX/com$JFAMX[1]), color="purple"))+
  geom_line(aes(x=Date, y=1000*(MOAT/com$MOAT[1]), color="green")) +
  geom_line(aes(x=Date, y=1000*(GSPC/com$GSPC[1]), color="yellow")) +
  labs(title = "Daily log return in FIVFX and indices", x="Time(daily)", y="Daily log return")
  
```

# Model linear regression
```{r}
fit <- lm(FIVFX_r ~ EEM_r + JFAMX_r + MOAT_r + GSPC_r, log)
summary(fit)
```

